Constraining Quiescent Supermassive Black Hole Environments.

### 2014-09-15 ms.tex
Updating one of the figures. And expanding captions.

\newcommand{\phirs}{\frac{G \Menc}{\rs}}
\newcommand{\soi}{\rm soi}
\newcommand{\rsoi}{r_{\soi}}
\newcommand{\ff}{\rm ff}
\newcommand{\tff}{t_{\ff}}
\newcommand{\rIa}{r_{\rm Ia}}
\newcommand{\sigsoi}{\sigma_{\soi}}

@@

\section{Solutions}
\subsection{Analytics: Flow properties at $\rs$}
It is possible to derive an analytic expression for the steady-state
stagnation radius, $\rs$, in terms of $v_w$ and the power law slope of
the density (at $\rs$) $n$.  We parameterize our results in terms of
$\vwOFH=\vwOFHexp$, $\Mbheight=\MbheightExp$ and
$\xi=\left(1+\frac{0.14 \Mbheight^{0.43}}{\vwOFH}\right)^{1/2}$ . $xi$
encapsulates the contribution of $\sigma$ in the heating.  We
summarize the main results here and place the detailed derivation in
Appendix~\ref{app:rs}.

@@

\begin{align}
  &\frac{\kb T}{\mu \mp}=\gammafi \kew \label{eq:tstag}\\
  &T=6 \times 10^6 {\rm K} \,  \,\ \vwO500^2 \xi^2 \mu
\end{align}

@@

\begin{align}
  &\rs=\frac{7}{2}\frac{G \Mbh}{n \vw^2}\\
  &\simeq 6 \, \pc \,\, \Mbheight \left(\vwOFH\right)^{-2}
  \label{eq:stag_simple}
\end{align}

@@

\begin{align}
  \rho(\rs)\simeq
  \begin{cases}
    2.6 \times 10^{-24} \Mbheight^{-0.14} \vwOFH^{-1} \xi^{-1} \eta \, {\rm g \, cm^{-3}}& \text{for cores}\\
    5.6 \times 10^{-24}  \Mbheight^{-0.56} \vwOFH  \xi^{-1}  \eta \, {\rm g \,cm^{-3}} & \text{for cusps}
  \end{cases}
  \label{eq:rhors}
\end{align}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{rs.eps}
  \caption{\label{fig:stag}$\x$ vs. $\vwNorm$}
\end{figure}

@@

\item \emph{Type Ia SNe} From he energy injected per Ia SNe,
  $E_{\rm Ia}$, and the SNe rate, $R_{\rm Ia}$

@@

@@

  \begin{align}
    t_{\rm Ia} \sim 2.5 \times 10^5 \Mseight^{-1} \; {\rm yrs}.
  \end{align}

@@

  \begin{figure}
    \includegraphics[width=\columnwidth]{vw-contour.eps}
    \caption{\label{fig:vweff} Overall $\vwO$ for $\Mbh$-Stellar Age parameter space.}
  \end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{mdot_mass.eps}
  \caption{\label{fig:mdot_mass}$\eddr$ vs. $\Mbh$}
\end{figure}

@@

\item \emph{NGC5813} %eta=0.1
  The observed density profile \citealt{RussellMcNamara+:2013a} is
  shallower than our calculated density profile, which has a sharp
  break at $\sim$0.1 kpc, the location of the break radius in the
  Nuker profile (this is the radius where the stellar light profile
  transitions from a shallower inner power law slope to a steeper
  outer power law slope.

>>>>

\newcommand{\phirs}{\frac{G \Menc}{\rs}}
\newcommand{\soi}{\rm soi}
\newcommand{\rsoi}{r_{\soi}}
\newcommand{\ff}{\rm ff}
\newcommand{\tff}{t_{\ff}}
\newcommand{\rIa}{r_{\rm Ia}}
\newcommand{\EIa}{E_{\rm Ia}}
\newcommand{\RateIa}{R_{\rm Ia}}
\newcommand{\sigsoi}{\sigma_{\soi}}

@@

\section{Solutions}
\subsection{Analytics: Flow properties at $\rs$}
It is possible to derive an analytic expression for the steady-state
stagnation radius, $\rs$, in terms of $v_w$ and the power law slope of
the density (at $\rs$) $n$.  We parameterize our results in terms of
$\vwOFH=\vwOFHexp$, $\Mbheight=\MbheightExp$ and
$\xi=\left(1+\frac{0.14 \Mbheight^{0.43}}{\vwOFH}\right)^{1/2}$. $\xi$
encapsulates the contribution of $\sigma$ in the heating.  We
summarize the main results here and place the detailed derivation in
Appendix~\ref{app:rs}.

@@

\begin{align}
  &\frac{\kb T}{\mu \mp}=\gammafi \kew \label{eq:tstag}\\
  &T=6 \times 10^6 {\rm K} \,  \,\ \vwOFH^2 \, \xi^2 \mu
\end{align}

@@

\begin{align}
  &\rs=\frac{7}{2}\frac{G \Mbh}{n \vwO^2}\\
  &\simeq 6 \, \pc \,\, \Mbheight \left(\vwOFH\right)^{-2}
  \label{eq:stag_simple}
\end{align}

@@

\begin{align}
  \rho(\rs)\simeq
  \begin{cases}
    2.6 \times 10^{-24} \Mbheight^{-0.14} \vwOFH^{-1} \xi^{-1} \eta \,
    \, {\rm g \, cm^{-3}}& \text{for cores}\\
    5.6 \times 10^{-24}  \Mbheight^{-0.56} \vwOFH  \xi  \eta \,\, {\rm g \,cm^{-3}} & \text{for cusps}
  \end{cases}
  \label{eq:rhors}
\end{align}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{rs.eps}
  \caption{\label{fig:stag} \emph{Top panel:} $\x$ vs. $\vwNorm$ for
    our sample for three different values of $\vwO$. Blue is
    $\vwO=1000$ km/s, orange is $\vwO=500$ km/s and green is
    $\vwO=200$ km/s. Squares correspond to cusp galaxies, while
    triangles correspond to cores. \emph{Bottom panel}: Fractional difference
    between numerical $x$ and the analytic result in
    Equation~\ref{eq:stag_analytic}. Points are colored in the same
    way as in the top panel.}
\end{figure}

@@

\item \emph{Type Ia SNe} From he energy injected per Ia SNe,
  $E_{\rm Ia}$, and the SNe rate (per stellar mass), $R_{\rm Ia}$

@@

  $\EIa \simeq10^{51}$ ergs. $\RateIa$ will depend on the age of the
  stellar population. $\eta$ can be calculated using
  Equation~\ref{eq:eta} in Appendix~\ref{app:eta}. $\RateIa$ may be
  calculated using the delay time distribution in
  \citealt{MaozMannucci+:2012a}. Generally, $\RateIa$ is the
  convolution of the star formation rate and the delay time
  distribution divided by the present stellar mass. In the limit of
  impulsive star formation, $\RateIa$ is the delay time distribution
  evaluated at the time since the star formation episode. The delay
  time distribution plotted in Figure 1 of
  \citealt{MaozMannucci+:2012a}, and has a functional form

  \begin{align}
    \Psi(\tau)=\frac{.03
      \left(\tau/10^8\right)^{-1.12}}{10^{10} \Msun}
  \end{align}

@@

  %AG--this would need to be adjusted to account for the delay time
  %distribution...
  \begin{align}
    t_{\rm Ia} \sim 2.5 \times 10^5 \Mseight^{-1} \; {\rm yrs}.
  \end{align}

@@

  \begin{figure}
    \includegraphics[width=\columnwidth]{vw-contour.eps}
    \caption{\label{fig:vweff} Overall $\vwO$ for $\Mbh$-Stellar Age
      parameter space. The contribution from stellar winds is taken to
      be $100$ km/s. The contribution from SNe Ia is calculated using
      Equation~\ref{eq:vw_sne}. The contribution from SNe Ia is only
      added if the $r_s$ corresponding to the resulting $\vwO$ is
      outside $\rIa$.}%describe other cases here.
  \end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{mdot_mass.eps}
  \caption{\label{fig:mdot_mass}$\eddr$ vs. $\Mbh$ for our sample. for
    our sample for three different values of $\vwO$. Blue is
    $\vwO=1000$ km/s, orange is $\vwO=500$ km/s and green is
    $\vwO=200$ km/s. Squares correspond to cusp galaxies, while
    triangles correspond to cores.}
\end{figure}

@@

\item \emph{NGC5813} %eta=0.1
  The observed density profile \citealt{RussellMcNamara+:2013a} is
  shallower than our calculated density profile, which has a sharp
  break at $\sim$0.1 kpc, the location of the break radius in the
  Nuker profile (this is the radius where the stellar light profile
  transitions from a shallower inner power law slope to a steeper
  outer power law slope).
